Opt-K

### 2013-03-12 paper/paper.tex
math mode

Within the discrete state space, the likelihood of an ensemble of
trajectories given the MSM is straightforward. We simply take the
product of the state to state transition probabilities along the path.
These state to state transition probabilities are our main central
parameters, the entries of the transition matrix. However, as we vary
the number of states, it is not permissible to simply compare these
likelihoods to select an optimal number of states. Doing so, we would
always chose the trivial model, with only one state, as the transition
probability in that model would be 1 and thus the likelihood of any
trajectory within that state space would be 1.

@@

Therefore, the most appropriate emmision distribution for discrete state
MSMs is that of the uniform distribution over the phase-space volume of
the state. That is, the likelihood of observing a conformation in phase
space given that the conformation is assigned to state \texttt{i} is 0
if the conformation is outside of the bounding volume of the state and
constant if the conformation is within the volume. The constant is set
so that the distribution integrates to 1, and is thus the reciprocal
volume of the microstate.

@@

To use this uniform distribution emission model, computationally, we
need to compute the volume of our MSM states, which are high-dimensional
Voronoi cells. While trivial in two or three dimensions, this
computational geometry task\\becomes challenging in large dimensional
settings.

>>>>

Within the discrete state space, the likelihood of an ensemble of
trajectories given the MSM is straightforward. We simply take the
product of the state to state transition probabilities along the path.
These state to state transition probabilities are our main central
parameters, the entries of the transition matrix. However, as we vary
the number of states, it is not permissible to simply compare these
likelihoods to select an optimal number of states. Doing so, we would
always chose the trivial model, with only one state, as the transition
probability in that model would be $1$ and thus the likelihood of any
trajectory within that state space would be $1$.

@@

Therefore, the most appropriate emmision distribution for discrete state
MSMs is that of the uniform distribution over the phase-space volume of
the state. That is, the likelihood of observing a conformation in phase
space given that the conformation is assigned to state $i$ is $0$
if the conformation is outside of the bounding volume of the state and
constant if the conformation is within the volume. The constant is set
so that the distribution integrates to $1$, and is thus the reciprocal
volume of the microstate.

@@

To use this uniform distribution emission model, computationally, we
need to compute the volume of our MSM states, which are high-dimensional
Voronoi cells. While trivial in two or three dimensions, this
computational geometry task becomes challenging in large dimensional
settings.
